Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-10 writing/embedded_meta_learning.tex
cutting length, hopefully improving clarity

\section{Introduction}
Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016, Marcus2018}. One fundamental reason for this is that humans are aware of what we are trying to compute and why. By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks. That is, neural networks knowledge about what is being computed is only implicitly accessible to those computations. \par
There are a number of advantages to representing knowledge about data and tasks together. In particular, it can grant the ability to rapidly adapt behavior to a new task. The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Vinyals2016, Finn2017a}. However, humans can take our knowledge and flexibly alter our behavior in accordance with a change in task demands or a single instruction. For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e. zero-shot). Deep learning systems at present generally lack this representational flexiblity. \par
In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e. mappings between tasks. For example, once a system has been trained to play a game, it should be able to alter its strategy in accordance with a change in task demands, such as trying to lose the game, or trying to play without using a certain action. The challenge is that the system must adapt to performing these tasks without seeing any data from the new task, only from either examples of similar transformations on different tasks (``here's how to change your go strategy to a losing one, here's how to change your checkers strategy to a losing one, now try to lose at chess'') or from natural language instructions (``try to lose at chess''). These mappings provide a new type of zero-shot transfer from one task to another -- the system must transform its behavior to adapt to a new task without ever having seen training data from that task. This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models. \par
To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.}. By treating task behaviors and data as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable. By embedding task behaviors, data, and language in the same space, we can conceptually think of both basic task solutions and adaptive functions, such as following instructions or altering behavior, as mappings in function space. This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing demands. We suggest that this ability will be key to building more intelligent and flexible deep learning systems. \par
In particular, we propose a meta-learning architecture which embeds data (including natural language inputs) and tasks in a shared space, and meta-learns to execute meta-mappings over this space. We demonstrate that this approach allows flexible remapping of behavior, as well as offering other benefits, such as a useful framework for continual learning. \par

\section{Meta-mappings}
We propose the challenge of meta-mappings, that is, mappings over tasks. These can take several flavors, including mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior). While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel. \par
We argue that these meta-mappings are a useful way to think about the flexibility that humans possess. For example, a system that learns to play go should be able to adapt to a different board size. These tasks clearly share a great deal of structure, and a human can easily transfer much of their knowledge from one board size to another without retraining, but deep learning models generally have no way of achieving this. Similarly, suppose an agent knows how to navigate from the airport to downtown. It should be able to adapt to changes of the environment such as street closures. We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose. While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not capture the extent of human flexibility. In particular, we can use our knowledge of a task to adapt to these type of task alterations zero-shot, that is, without seeing a single example from the new task. \par
In the machine-learning setting, these mappings can be cued in different ways, for example by examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to change your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board''). Achieving this kind of flexibility will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen. \par

\section{Embedded Meta-Learning (EML) architecture}
To achieve this, we propose a new class of Embedded Meta-Learning (EML) architectures which consist of two parts: 
\begin{enumerate}
\item Domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
\item A meta-learning system which:
    \begin{enumerate}
    \item Embeds tasks into the shared embedding space $Z$.
    \item Learns to perform tasks in accordance with their embeddings.
    \end{enumerate}
\end{enumerate}
The utility of having a completely shared space $Z$ in which data, language, and tasks are represented is that it allows for arbitrary mappings between these distinct types of data. In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explaining behavior), or tasks to tasks (changing behavior based on examples). This is a step closer to the flexible reasoning humans display. \par
Without training on these mappings, of course, the system will not be able to execute them well. However, if it is trained on a braod enough set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution, as we demonstrate below. For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however. This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow. \par 
\begin{figure}
\centering
\begin{tikzpicture}[auto, scale=0.9]
\node [dashblock] at (0, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: \textbf{Shared} \\ \textbf{representation}\end{tabular}};

@@

\node [dashblock] at (0, -2.5) (collection) {
\(\left\{
\begin{matrix}
(\text{in}_0, \text{out}_0),\\
(\text{in}_1, \text{out}_1),\\
$\vdots$
\end{matrix}\right\}\)};
\path [line] (rep.south) to (collection);
\path [line] ([xshift=-1em]rep.south) to (collection);
\path [line] ([xshift=1em]rep.south) to (collection);

@@

\end{tikzpicture}
\caption{Schematic of our general architecure. Blocks with solid edges denote deep networks with learnable parameters, dashed edges represent inputs, outputs, embeddings, etc., and $f$ is a deep network with parameters specified by $\mathcal{H}$. Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g. both language and vision.} \label{architecture_fig}
\end{figure}
More formally, we take a \emph{functional} perspective on learning. A datum can be represented by a constant function which outputs it. (For example, each point in the latent space of an autoencoder can be thought of this way.) This allows us to interpret model inputs or outputs as functions. We can then interpret most machine learning tasks as a mapping of functions to functions. These functions could represent data\footnote{Where ``data'' is a quite flexible term. The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, or they could be functions that operate on functions themselves. Under this perspective, learning tasks and learning to flexibly map between tasks, or learning to map from language to tasks, are all the same type of problem. \par
Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$. Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$. Outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$. Targets are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$. (Targets do not necessarily need to be output-like, e.g. in our RL tasks, we use (action, outcome) tuples as ``targets.'') \par
Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to the (embedded) targets. These transformations are performed by a system with the following components:  
\begin{itemize}
\item $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding. 
\item $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which takes a function embedding and produces a set of parameters. 
\item $f: Z \rightarrow Z$ -- the transformation, implemented by a deep network with parameters specified by $\mathcal{H}$.
\end{itemize}
See Fig. \ref{architecture_fig} for a schematic of the architecture. \par

\subsection{Operation}
A basic forward pass through the system might look as follows.
\begin{enumerate}
\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings. Another set of (possibly unlabeled) inputs is provided and embedded.
\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
\end{enumerate}
To write this explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ for which we wish to generate a predicted output $\hat{y}$. This output would be generated as follows: 
\[\hat{y} = \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ... \right\}\right)\right)\]
This system can be trained end-to-end if labels are provided for the second set of inputs. In particular, suppose we have some loss function $\mathcal{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$. We define our total loss computed on some dataset $D_2$ as:
\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
More generally, suppose we have some input which is already embedded in the representation space $z_{in} \in Z$, and a task/function embedding $z_{\text{function}} \in Z$. Then we can generate an output $\hat{z}_{out} \in Z$ as:  
\[\hat{z}_{out} = f_{z_{\text{function}}}(z_{in}) \qquad \text{where } f_{z_{\text{function}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{function}}\right)\]
This output can then be appropriately dispatched depending on the task at hand. For example, if the $z_{in,i}$ are the system's embeddings for trying to win various games, and the $z_{out,i}$ are the corresponding embeddings for trying to lose those games, then $z_{out}$ could be interpreted as the system's guess at a losing strategy for the game embedded as $z_{in}$, and then could be used to play that game. We could then evaluate performance by how well the system actually performs at losing with the $z_{out}$ strategy. \par
Similarly, we could map from language to a task embedding, and then ask how well the system performs at the task specified by language. The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows substantial flexibility within a unified framework.

@@

\subsection{Continual learning}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks. Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well. Error-bars are bootstrap 95\%-CIs.}
\label{poly_continual_results}
\end{figure}
Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example of a task it has seen at each inference step. We would like to be able to store our knowledge about the tasks in a way that allows it to be more carefully refined. Furthermore, we would like the system to be able to adapt to new tasks (that it cannot perfectly solve from examples) without catastrophically interfering with our prior knowledge \citep{McCloskey1989}. \par
A very simple solution to these problems is naturally suggested by our architecture. Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step. This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task. That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par 
To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks. We trained on these new tasks by starting from the meta-learning network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters. The results are shown in fig. \ref{poly_continual_results}. The meta-network embeddings offers good immediate performance, and substantially accelerates the optimization the process, compared to a randomly-initialized embedding (see supp. fig. \ref{supp_poly_continual_results} for a more direct comparison). Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network. \par

@@

\caption{Basic meta learning in the cards domain. (a) The system successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out. The gray dashed line indicates chance performance, while the solid lines are optimal performance. The colored dashed lines show how well the system could perform by playing the strategy from the most correlated game it has seen. The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest one. (b) The system can rapidly adapt to new tasks. (This figure shows the effect of training all parameters while replaying old tasks, unlike the continual learning strategy above.) Error-bars are bootstrap 95\%-CIs.}

@@

We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions. We hope that our work will inspire more exploration of behavior adaptation, especially in tasks beyond the simple domains we considered here. For example, as we alluded to above, tasks such as visual question-answering \citep[e.g.][]{Antol2015} can be usefully interpreted from this perspective (a question essentially yields a function from images to answers, and there are many systematic relationships between these functions), as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017, Co-Reyes2019}. Furthermore, we think our work provides a novel perspective on the types of flexibility that human intelligence exhibits, and thus hope that it may have implications for cognitive science. \par 

@@

\subsubsection{Card games}
\label{meth_data_cards}
Our card games were played with two suits, and 4 values per suit. In our setup, each hand in a game has a win probability (proportional to how it ranks against all other possible hands). The agent is dealt a hand, and then has to choose to bet 0, 1, or 2 (the three actions it has available). We considered a variety of games which depend on different features of the hand: 
\begin{itemize}
\item \textbf{High card:} Highest card wins.
\item \textbf{Pairs} Same as high card, except pairs are more valuable, and same suit pairs are even more valuable.
\item \textbf{Straight flush:} Most valuable is adjacent numbers in same suit, i.e. 4 and 3 in most valuable suit wins every time (royal flush).
\item \textbf{Match:} the hand with cards that differ least in value (suit counts as 0.5 pt difference) wins.
\item \textbf{Blackjack:} The hand's value increases with the sum of the cards until it crosses 5, at which point the player ``goes bust,'' and the value becomes negative. 
\end{itemize}
We also considered three binary attributes that could be altered to produce variants of these games:
\begin{itemize}
\item \textbf{Losers:} Try to lose instead of winning! Reverses the ranking of hands.
\item \textbf{Suits rule:} Instead of suits being less important than values, they are more important (essentially flipping the role of suit and value in most games).
\item \textbf{Switch suit:} Switches which of the suits is more valuable.
\end{itemize}
Any combination of these options can be applied to any of the 5 games, yielding 40 possible games. The systems were trained with the full 40 possible games, but after training we discovered that the ``suits rule'' option does not substantially alter the games we chose (in the sense that the probability of a hand winning in the two variants of a game is very highly correlated), so we have omitted it from our analyses.\par
\textbf{Meta-tasks:} For meta-tasks, we gave the network 8 task-embedding classification tasks (one-vs-all classification of each of the 5 game types, and of each of the 3 attributes), and 3 meta-mapping tasks (each of the 3 attributes).
\subsection{Model \& training}

@@

\begin{tabular}{|c|ccc|}

@@

& \phantom{bla}Polynomials\phantom{la} & Continual learning & \phantom{blahb}Cards\phantom{blahb} \\

@@

$Z$-dimension & 512 & 512 & 512 \\
$\mathcal{I}$ num. layers & \multicolumn{3}{c|}{3} \\ 
$\mathcal{I}$ num. hidden units & \multicolumn{3}{c|}{64} \\ 
$\mathcal{O}$ num. layers & 1 & 1 & 3 \\ 
$\mathcal{O}$ num. hidden units & - & - & 512 \\ 
$\mathcal{T}$ num. layers & \multicolumn{3}{c|}{1} \\ 
$\mathcal{M}$ architecture & \multicolumn{3}{c|}{2 layers per-datum, max pool across, 2 layers} \\ 
$\mathcal{H}$ architecture & \multicolumn{3}{c|}{4 layers} \\ 
$\mathcal{M}, \mathcal{H}$ num. hidden units & \multicolumn{3}{c|}{512} \\ 
$f$ architecture & \multicolumn{3}{c|}{4 layers} \\ 
$f$ num. hidden units & \multicolumn{3}{c|}{64} \\ 

>>>>

\section{Introduction}
Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016, Marcus2018}. One fundamental reason for this is that humans are aware of what we are trying to compute and why. By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks. That is, neural networks knowledge about what is being computed is only implicitly accessible to those computations. \par
There are a number of advantages to representing knowledge about data and tasks together. In particular, it can grant the ability to rapidly adapt behavior to a new task. The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Vinyals2016, Finn2017a}. However, humans can take our knowledge and flexibly alter our behavior in accordance with a change in task demands or a single instruction. For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e. zero-shot). Deep learning systems at present generally lack this representational flexiblity. \par
In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e. mappings between tasks (see below). This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models. To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.}. By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable. This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing demands. We demonstrate that this approach allows flexible remapping of behavior, as well as offering other benefits, such as a useful framework for continual learning. We suggest that approaches like this will be key to building more intelligent and flexible deep learning systems. \par

\section{Meta-mappings}
We propose the challenge of meta-mappings, that is, mappings where an input or output (or both) is a task. These can take several flavors, including mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior). While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel. \par
We argue that these meta-mappings are a useful way to think about the flexibility that humans possess. For example, a system that learns to play go should be able to adapt to a different board size. These tasks clearly share a great deal of structure, and a human can easily transfer much of their knowledge from one board size to another without retraining, but deep learning models generally have no way of achieving this. Similarly, suppose an agent knows how to navigate from the airport to downtown. It should be able to adapt to changes of the environment such as street closures. We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose. While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not capture the extent of human flexibility. In particular, we can use our knowledge of a task to adapt to these type of task alterations zero-shot, that is, without seeing a single example from the new task. \par
In the machine-learning setting, these mappings can be cued in different ways, for example by examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to change your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board''). Achieving this kind of flexibility will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen. \par

\section{Embedded Meta-Learning (EML) architecture}
To achieve this, we propose a new class of Embedded Meta-Learning (EML) architectures which consist of two parts: 
\vspace{-0.75em}
\begin{enumerate} \setlength \itemsep{0em}
\item An input/output system: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
\item A meta-learning system which embeds tasks into the shared embedding space $Z$, and learns to perform tasks in accordance with their embeddings.
\end{enumerate}
\vspace{-0.75em}
The utility of having a completely shared space $Z$ in which data, language, and tasks are represented is that it allows for arbitrary mappings between these distinct types of data. In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explaining behavior), or tasks to tasks (changing behavior based on examples). This is a step closer to the flexible reasoning humans display. \par
Without training on these mappings, of course, the system will not be able to execute them well. However, if it is trained on a broad enough set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution, as we demonstrate below. For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however. This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow. \par 
\begin{figure}
\centering
\begin{tikzpicture}[auto, scale=0.75]
\node [dashblock] at (0, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: \textbf{Shared} \\ \textbf{representation}\end{tabular}};

@@

\node [dashblock] at (0, -2.5) (collection) {
\(\left\{
\begin{matrix}
(z_{in,0}, z_{out,0}),\\
(z_{in,1}, z_{out,1}),\\
$\vdots$
\end{matrix}\right\}\)};
\path [line] (rep.south) to (collection);
\path [line] ([xshift=-1em]rep.south) to (collection);
\path [line] ([xshift=1em]rep.south) to (collection);

@@

\end{tikzpicture}
\caption{Schematic of our general architecure. Blocks with solid edges denote deep networks with learnable parameters, dashed edges represent inputs, outputs, embeddings, etc., and $f$ is a deep network with parameters specified by $\mathcal{H}$. Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g. both language and vision.} \label{architecture_fig}
\end{figure}
More formally, we take a \emph{functional} perspective on learning. A datum can be represented by a constant function which outputs it. (For example, each point in the latent space of an autoencoder can be thought of this way.) This allows us to interpret model inputs or outputs as functions. We can then interpret most machine learning tasks as a mapping of functions to functions. The key insight is that, while these mappings could be over functions that represent data\footnote{Where ``data'' is a quite flexible term. The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, they could also operate on task-mappings themselves. This is related to the idea of a homoiconic programming language, where programs can be manipulated like data. Under this perspective, learning tasks, learning to map from language to tasks, and learning to flexibly transform between tasks, are all the same type of problem. \par
Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$. Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$. Outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$. Targets are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$. \par
Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to the (embedded) targets. These transformations are performed by a system with the following components (see Fig. \ref{architecture_fig} for a schematic):  
\vspace{-0.75em}
\begin{itemize} \setlength\itemsep{0em}
\item $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding. 
\item $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which maps a function embedding to parameters. 
\item $f: Z \rightarrow Z$ -- the transformation, implemented by a deep network parameterized by $\mathcal{H}$.
\end{itemize}
\vspace{-0.75em}
A basic forward pass through the system would proceed as follows. First, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$. Some of these examples are fed to $\mathcal{M}$ to produce a function embedding (the remainder can be unlabeled during inference, or held-out to avoid memorization during training). This function embedding is mapped through $\mathcal{H}$ to parameterize $f$, and then $f$ is used to process the remaining examples, and $\mathcal{O}$ to map the resultant embeddings to outputs. This system can be trained end-to-end. See appendix \ref{app_model_details} for detailed, architecture, operation, and hyper-parameters. \par

To write this explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ for which we wish to generate a predicted output $\hat{y}$. This output would be generated as follows: 
\[\hat{y} = \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ... \right\}\right)\right)\]
This system can be trained end-to-end if labels are provided for the second set of inputs. In particular, suppose we have some loss function $\mathcal{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$. We define our total loss computed on some dataset $D_2$ as:
\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
More generally, suppose we have some input which is already embedded in the representation space $z_{in} \in Z$, and a task/function embedding $z_{\text{function}} \in Z$. Then we can generate an output $\hat{z}_{out} \in Z$ as:  
\[\hat{z}_{out} = f_{z_{\text{function}}}(z_{in}) \qquad \text{where } f_{z_{\text{function}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{function}}\right)\]
This output can then be appropriately dispatched depending on the task at hand. For example, if the $z_{in,i}$ are the system's embeddings for trying to win various games, and the $z_{out,i}$ are the corresponding embeddings for trying to lose those games, then $z_{out}$ could be interpreted as the system's guess at a losing strategy for the game embedded as $z_{in}$, and then could be used to play that game. We could then evaluate performance by how well the system actually performs at losing with the $z_{out}$ strategy. \par
Similarly, we could map from language to a task embedding, and then ask how well the system performs at the task specified by language. The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows substantial flexibility within a unified framework.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks. Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well. Error-bars are bootstrap 95\%-CIs.}
\label{poly_continual_results}
\end{figure}
\textbf{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example of a task it has seen at each inference step. We would like to be able to store our knowledge about the tasks in a way that allows it to be more carefully refined. Furthermore, we would like the system to be able to adapt to new tasks (that it cannot perfectly solve from examples) without catastrophically interfering with our prior knowledge \citep{McCloskey1989}. \par
A very simple solution to these problems is naturally suggested by our architecture. Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step. This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task. That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par 
To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks. We trained on these new tasks by starting from the meta-learning network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters. The results are shown in fig. \ref{poly_continual_results}. The meta-network embeddings offers good immediate performance, and substantially accelerates the optimization the process, compared to a randomly-initialized embedding (see supp. fig. \ref{supp_poly_continual_results} for a more direct comparison). Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network. \par

@@

\caption{Basic meta learning in the cards domain. (a) The system successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out. The gray dashed line indicates chance performance, while the solid lines are optimal performance. The colored dashed lines show how well the system could perform by playing the strategy from the most correlated trained task. The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest. (b) The system can rapidly adapt to new tasks. (This figure shows the effect of training all parameters while replaying old tasks, unlike the continual learning strategy above.) Error-bars are bootstrap 95\%-CIs.}

@@

We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions. We hope that our work will inspire more exploration of behavior adaptation, especially in tasks beyond the simple domains we considered here. To this end, we suggest the creation of meta-learning datasets which include information not only about tasks, but about the relationships between them. For example, as we alluded to above, tasks such as visual question-answering \citep[e.g.][]{Antol2015} can be usefully interpreted from this perspective (a question essentially yields a function from images to answers, and there are many systematic relationships between these functions), as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017, Co-Reyes2019}. Furthermore, we think our work provides a novel perspective on the types of flexibility that human intelligence exhibits, and thus hope that it may have implications for cognitive science. \par 

@@

\subsubsection{Card games}
\label{meth_data_cards}
Our card games were played with two suits, and 4 values per suit. In our setup, each hand in a game has a win probability (proportional to how it ranks against all other possible hands). The agent is dealt a hand, and then has to choose to bet 0, 1, or 2 (the three actions it has available). We considered a variety of games which depend on different features of the hand: 
\begin{itemize}
\item \textbf{High card:} Highest card wins.
\item \textbf{Pairs} Same as high card, except pairs are more valuable, and same suit pairs are even more valuable.
\item \textbf{Straight flush:} Most valuable is adjacent numbers in same suit, i.e. 4 and 3 in most valuable suit wins every time (royal flush).
\item \textbf{Match:} the hand with cards that differ least in value (suit counts as 0.5 pt difference) wins.
\item \textbf{Blackjack:} The hand's value increases with the sum of the cards until it crosses 5, at which point the player ``goes bust,'' and the value becomes negative. 
\end{itemize}
We also considered three binary attributes that could be altered to produce variants of these games:
\begin{itemize}
\item \textbf{Losers:} Try to lose instead of winning! Reverses the ranking of hands.
\item \textbf{Suits rule:} Instead of suits being less important than values, they are more important (essentially flipping the role of suit and value in most games).
\item \textbf{Switch suit:} Switches which of the suits is more valuable.
\end{itemize}
Any combination of these options can be applied to any of the 5 games, yielding 40 possible games. The systems were trained with the full 40 possible games, but after training we discovered that the ``suits rule'' option does not substantially alter the games we chose (in the sense that the probability of a hand winning in the two variants of a game is very highly correlated), so we have omitted it from our analyses.\par
\textbf{Meta-tasks:} For meta-tasks, we gave the network 8 task-embedding classification tasks (one-vs-all classification of each of the 5 game types, and of each of the 3 attributes), and 3 meta-mapping tasks (each of the 3 attributes).
\subsection{Model \& training} \label{app_model_details}
Basic task operation:
\begin{enumerate}
\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings. Another set of (possibly unlabeled) inputs is provided and embedded.
\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
\item The system is trained end-to-end to minimize the loss on these outputs.
\end{enumerate}
Meta-task operation:
\begin{enumerate}
\item A meta-dataset of (input, target) task embeddings is collected. Another set (possibly only inputs) is provided.
\item The meta network $\mathcal{M}$ maps this set of (input, target) task-embedding pairs to a function embedding.
\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
\item The system is trained to minimize $\ell_2$ loss between these mapped embeddings and the target embeddings. 
\end{enumerate}
Note that there are two kinds of hold-out in the training of this system. First, some of the trained tasks are held-out on each training step, in order to force the system to generalize rather than just memorize. Second, there are truly held-out tasks that the system has never seen in training, these are the held-out tasks and meta-mappings that we evaluate on at the end of training.

\subsubsection{Detailed hyper-parameters}

@@

\begin{tabular}{|c||c|c|c|}

@@

& \phantom{bla}Polynomials\phantom{la} & Continual learning & \phantom{blahb}Cards\phantom{blahb} \\\hline

@@

$Z$-dimension & 512 & 512 & 512 \\\hline
$\mathcal{I}$ num. layers & \multicolumn{3}{c|}{3} \\\hline 
$\mathcal{I}$ num. hidden units & \multicolumn{3}{c|}{64} \\\hline 
$\mathcal{O}$ num. layers & 1 & 1 & 3 \\\hline 
$\mathcal{O}$ num. hidden units & - & - & 512 \\\hline 
$\mathcal{T}$ num. layers & \multicolumn{3}{c|}{1} \\\hline 
$\mathcal{M}$ architecture & \multicolumn{3}{c|}{2 layers per-datum, max pool across, 2 layers} \\\hline 
$\mathcal{H}$ architecture & \multicolumn{3}{c|}{4 layers} \\\hline 
$\mathcal{M}, \mathcal{H}$ num. hidden units & \multicolumn{3}{c|}{512} \\\hline 
$f$ architecture & \multicolumn{3}{c|}{4 layers} \\\hline 
